NFC and burnout in teachers - A replication and extension study

### 2021-10-26 Manuscript/Manuscript.Rmd
corrected cursive characters in table

  desc_table <-
  kbl(correlations,
      booktabs = T, # no vertical lines
      escape = F, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = F, # correctly print special characters
             threeparttable = T) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "Effect" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "SE" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "z-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "p-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",6))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, SE = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

>>>>

  desc_table <-
  kbl(correlations,
      booktabs = TRUE, # no vertical lines
      escape = FALSE, # correctly print special characters
      align = rep("l",14)) %>% # left aligns the text in every column
    kable_styling(latex_options = c("striped", "scale_down")) %>%
    footnote(general = "MBI = Maslach Burnout Inventory, MBI EE = Emotional exhaustion subscale, MBI DP = Depersonalisation subscale, MBI RPE = Reduced personal efficacy subscale, ERQ = Emotion Regulation Questionnaire, ERQ S = Suppression subscale, ERQ R = Reappraisal subscale, SCS = Self-Control Scale, NFC = Need for Cognition, DTH = Demands Too High, DTL = Demands Too Low, DRF = Demand-Resource-Fit, COV = Covid-19 Burden. \\\\textit{N} = 180. * \\\\textit{p} < .05. ** \\\\textit{p} < .01. *** \\\\textit{p} < .001. Diagonal is Cronbach's Alpha and (in brackets) MacDonald's Omega.",
             escape = FALSE, # correctly print special characters
             threeparttable = TRUE) %>% # line breaks in the footnote
  kableExtra::landscape() # make the table horizontal

@@

  fit_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fit_summ$PE$est[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fit_summ$PE$se[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fit_summ$PE$z[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fit_summ$PE$pvalue[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fit_summ$PE$ci.lower[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fit_summ$PE$ci.upper[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fit_summ$PE$std.all[fit_summ$PE$label != "" & fit_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

@@

  replication_table <-
    kbl(fit_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 8, 10) %>%
    pack_rows("Total Effect", 11, 11) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

```{r objective1years_table, echo=FALSE, message=FALSE, warning=FALSE}

  fityears_table <- data.frame("Path" = c("NFC $\\rightarrow$ Self Control", "Years spent teaching $\\rightarrow$ Self Control", "NFC $\\rightarrow$ Reappraisal", "NFC $\\rightarrow$ Suppression",
                                   "Self Control $\\rightarrow$ RPE", "Reappraisal $\\rightarrow$ RPE", "Suppression $\\rightarrow$ RPE", "NFC $\\rightarrow$ RPE",
                                   "NFC $\\rightarrow$ RPE via Self Control", "NFC $\\rightarrow$ RPE via Reappraisal", "NFC $\\rightarrow$ RPE via Suppression",
                                   "Total Effect"),
                          "$B$" = c(fityears_summ$PE$est[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$SE$" = c(fityears_summ$PE$se[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$z$-value" = c(fityears_summ$PE$z[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$p$-value" = c(fityears_summ$PE$pvalue[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Lower" = c(fityears_summ$PE$ci.lower[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "CI Upper" = c(fityears_summ$PE$ci.upper[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          "$\\beta$" = c(fityears_summ$PE$std.all[fityears_summ$PE$label != "" & fityears_summ$PE$label != "Contrast"]),
                          check.names = FALSE)

  fityears_table[2:ncol(fityears_table)] <- format(round(fityears_table[2:ncol(fityears_table)], digits = 3), nsmall = 2)

  replicationyears_table <-
    kbl(fityears_table,
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    pack_rows("Direct Effects", 1, 8) %>% # group the rows and add a header in between
    pack_rows("Indirect Effects", 9, 11) %>%
    pack_rows("Total Effect", 12, 12) %>%
    footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
```
